Succinct representations for abstract interpretation

### 2011-11-01 papers/PLDI2012/implicitization.tex
Encore des remarques.

\MM{À changer si on décide de ne plus distinguer $X^s$ et $X^d$}

Also, to prevent the algorithm from adding too many paths at a time,
and in particular to prevent the algorithm from trying to re-add the
same path infinitely many times, we use another abstract value
associated to a control point $p_j$, noted $X_j^d$, which is distinct
from $X_j^s$, and initialized to $X_j^s$. This value is updated when a
point $p_j$ is the target of a new path, and is used instead of
$X_j^s$ in the SMT formula. We thus check the satisfiability of the formula
$f'(p_i)$, where:
$$f'(p_i) = \rho \wedge b_i^s \wedge 
\displaystyle\bigwedge_{j \in P_R \atop j \neq i} \neg
b_j^s \wedge X_i^s \wedge \displaystyle\bigvee_{j \in Succ(i)} (b_j^d \wedge
\neg X_j^d)$$

@@

The $\sigma_i$ functions take as parameters the index of the starting abstract
value, and the path we focus on. If we dynamically construct these functions
during the analysis, we should store the results of the $\sigma_i$ functions into a
compact representation, such as Algebraic Decision Diagrams.
Note that $\sigma_i(j,k)$ will be computed only if needed.

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
We start with one single
disjunct per control point ($m_i=1$ for each $i, p_i \in P_R$) 
and empty maps $\sigma_i$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma_i(j,k)$ is then constructed on the fly only when needed.
When $\sigma_i(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}

>>>>

% À changer si on décide de ne plus distinguer $X^s$ et $X^d$
Also, to prevent the algorithm from adding too many paths at a time,
and in particular to prevent the algorithm from trying to re-add the
same path infinitely many times, we use another abstract value
associated to a control point $p_j$, noted $X_j^d$, which is distinct
from $X_j^s$, and initialized to $X_j^s$. This value is updated when a
point $p_j$ is the target of a new path, and is used instead of
$X_j^s$ in the SMT formula. We thus check the satisfiability of the formula
$f'(p_i)$, where:
$$f'(p_i) = \rho \wedge b_i^s \wedge 
\displaystyle\bigwedge_{j \in P_R \atop j \neq i} \neg
b_j^s \wedge X_i^s \wedge \displaystyle\bigvee_{j \in Succ(i)} (b_j^d \wedge
\neg X_j^d)$$

@@

The $\sigma_i$ functions take as parameters the index of the starting abstract
value, and the path we focus on. If we dynamically construct these functions
during the analysis, we should store the results of the $\sigma_i$ functions into a
compact representation, such as Algebraic Decision Diagrams.\MM{Du
  coup, j'aurais intégré cette phrase au paragraphe suivant. C'est des
  ADD que tu utilises finalement ?}
Note that $\sigma_i(j,k)$ will be computed only if needed.

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
We start with one single
disjunct per control point ($m_i=1$ for each $i, p_i \in P_R$) 
and empty maps $\sigma_i$.
$M$ denotes an upper bound on the number of disjuncts per control point.
$\sigma_i(j,k)$ is then constructed on the fly only when needed.
When $\sigma_i(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}
